Recurrent Neural Networks for object detection

### 2019-07-01 Paper/Paper_First_Draft.tex
Added section Flow Networks

\subsection{Deep Feature Flow for Video Recognition}
ToDo

>>>>

\subsection{Deep Feature Flow for Video Recognition}
Zhu, Xiong, Dai, Yuan and Wei develop in [2] a way to use flow nets to detect objects in video frames. As shown in figure 10 their architecture consists of three main parts: A network to create visual features, a network to create class probabilities and bounding boxes out of feature maps, and a network which estimates the optical flow. \newline

\begin{figure} [h]
\includegraphics[width=\columnwidth]{Flow}
\caption{Architecture Deep Feature Flow for Video Recognition}
\end{figure}

The paper differs between key frames and other frames. The network to create visual features $ N_{feat} $ only processes on key frames. It is a fully convolutional network, which takes as an input the image and outputs a feature maps. As a feature network they use a pretrained version of ResNet. \newline

The second network $ N_{task} $ does the recognition task over the feature maps. It performs on every frame.  Zhu, Xiong, Dai, Yuan and Wei use an R-FCN network for the recognition task.  \newline

For all non-key frames the feature maps are not constructed by the feature network. Instead, they are propagated by a flow network $ N_{flow} $.  Zhu, Xiong, Dai, Yuan and Wei use a state-of-the-art CNN based FlowNet architecture as a flow network. The flow estimation is given by: \newline

$ f_{i} =  W (f_{k},M_{i->k}, S_{i->k})$ \newline

$ f_{k} $ is the key frame's feature map, $ M_{i->k} $ is a two dimensional flow field, it projects back the location of an object in the current frame to the location in the key frame by using bilinear interpolation and  $ S_{i->k} $ is scale field. \newline

Zhu, Xiong, Dai, Yuan and Wei use a fixed key frame scheduling and they already see a potential improvement in changing the key frame policy.
